Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-25 Grassmannian_cells.tex
Section 3.2 edits and notation changes (not completed)

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{{\underline i}}
\newcommand{\uj}{{\underline j}}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

Let $W_Q$ be the free non-abelian group generated by $Q_1$.  
Write $A_Q\cong \ZZ^{Q_1}$ for the free abelian group generated by $Q_1$ and denote by $e_\alpha\in A_Q$ the generator corresponding to $\alpha\in Q_1$. 
\begin{definition}
  The \emph{universal abelian covering quiver} $\hat Q$ of $Q$ has vertices $\hat Q_0=Q_0\times A_Q$ and arrows $\hat Q_1=Q_1\times A_Q$, where $(\alpha,\chi):\big(s(\alpha),\chi\big)\to\big(t(\alpha),\chi+e_\alpha\big)$ for $\alpha\in Q_1$ and $\chi\in A_Q$.
  Write $F_Q:\rep \hat Q\to\rep Q$ for the natural functor.

@@

We will mainly be interested in particular lifts $\tilde P_m$ of the preprojective representations $P_m$ of $K(n)$ to the universal cover $\widetilde{K(n)}$.
First, recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
The preprojective lifts we use are defined by the following analogue of the recursions of Remark~\ref{rem:reflection recursion}.
\begin{itemize}
  \item For $m=1$, we consider the lift $\tilde P_1$ satisfying $\dim(\tilde P_1)_{(1,1)}=1$ and $\dim (\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,1)$.
  \item For $m=2$, we consider the lift $\tilde P_2$ satisfying $\dim (\tilde P_2)_{(2,1)}=\dim (\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\dim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,1),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
  \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
    More precisely, we set
    \begin{align}
      \label{eq:recursive covers}
      \tilde P_m:=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
    \end{align}
\end{itemize}

It will be rather important that our chosen lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation $\tilde P_m$ by the action of $w\in W_n$.
To simplify the notation, we abbreviate $\tilde P_{2l-1,i}:=\tilde P_{2l-1,\alpha_i}$ and $\tilde P_{2l,i}:=\tilde P_{2l,\alpha_i^{-1}}$.
\begin{lemma}
  For each $m\ge1$, the representation $\tilde P_{m+1}$ has precisely $n$ subrepresentations covering $P_m$.
  These are the representations $\tilde P_{m,i}$ corresponding to the $n$ different arrows of $K(n)$. 
\end{lemma}
\begin{proof}
  This is clear for $m=1$ and follows in general by applying the identities \eqref{eq:recursive covers}.
\end{proof}
\begin{remark}
  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric.
  In particular, they all have the same middle vertex $(1,1)$ if $m$ is odd and middle vertex $(2,1)$ if $m$ is even.
\end{remark}

Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
For $l\ge1$, set
\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\}\}.\]
Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$ we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
More precisely, we obtain a sequence of preprojective representations which uniquely determines the desired inclusion:
\[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \ses{\bigoplus_{i\in I} \tilde P_{m,i}}{\tilde P_{m+1}}{\tilde P_{m+1}^I}.
      \end{equation}
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  The first part is immediate from Theorem~\ref{covering}.
  The second part is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC=\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

  For the final claim, observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to a subspace $V\in H_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$.
\end{proof}
In the following, we make use of this lemma and fix a basis of $\Hom(P_m,P_{m+1})$ which is compatible with the direct sum decomposition from part (1).
\begin{lemma}
  \label{le:properties}
  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
  \begin{enumerate}
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\notin I$, in which case 
      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})=\CC.\] 
    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)=\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
    \item We have $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
  where the final zero follows from Lemma~\ref{le:homdecomposition}(2).
  Now the middle space is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).

  Part (2) is an immediate consequence of Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering} or can be obtained directly by applying $\Hom(\tilde P_{m+1},-)$ to the sequence \eqref{ses1}.
  Part (3) then follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1}.
\end{proof}

Note that by Lemma~\ref{le:properties}(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
\[\ses{\bigoplus_{i\in J\setminus I}\tilde P_{m,i}}{\tilde P_m^I}{\tilde P_{m+1}^J}.\]

%Let $$I_s=\{(j_1,\ldots,j_s)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
That is, taking $\varepsilon=(-1)^{m+1}$ we quotient out the translations $\tilde P_{m,w\alpha_i^\varepsilon}$ for $i\in I$.
These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.

\begin{example}\label{smallm}[The cases $m=2,3,4$]
\end{example}

As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$, they are uniquely determined by their dimension vector.
We use this fact and do not state the particular maps defining the lifts.
In this example, we just state the support of the representation including those dimensions which are not one.
We call it the quiver of the representations.

The representation $\tilde P_2$ is defined by the following quiver:
\begin{align*}
  \xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\(2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n}}[rrd] &&\vdots\\&&(1,\alpha_n)}
\end{align*}
The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$, can be obtained from this quiver by erasing the arrow $\alpha_i$ and the corresponding sink. In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $\alpha_{j_1},\ldots,\alpha_{j_l}$ and the corresponding sinks.

The representation $\tilde P_3$ is given by the quiver
	\begin{align*}
          \xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{\alpha_1}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{\alpha_n}[llu]}
        \end{align*}
	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.  Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one. We assume that $(j_1,\ldots,j_l)=(1,\ldots,l)$ which is no restriction as the general case can be obtained by relabelling. 
The Auslander-Reiten translate $\tau\tilde P_{3}^{(1,\ldots,l)}$ is given by
	\begin{align*}
          \xymatrix@R10pt@C20pt{&&(2,\alpha_{l+1}^{-1})\ar_{\alpha_{l+1}}[lld]\\(1,1) &&\vdots\\&&(2,\alpha_{n}^{-1})\ar_{\alpha_{n}}[llu]}
        \end{align*}
In particular, the image of the unique homomorphism $\tilde P_{2,i}=\alpha^{-1}_i.\tilde P_2\to\tau\tilde P_{3}^{(1,\ldots,l)}$ has image $(2,\alpha_{i}^{-1})\xrightarrow{\alpha_{i}}(1,1)$ for $i=l+1,\ldots,n$.

>>>>

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{{\underline i}}
\newcommand{\uj}{{\underline j}}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

Let $W_Q$ be the free non-abelian group generated by $Q_1$.  
Write $A_Q\cong \ZZ^{Q_1}$ for the free abelian group generated by $Q_1$ and denote by $e_\alpha\in A_Q$ the generator corresponding to $\alpha\in Q_1$. 
\begin{definition}
  \label{def:covering quivers}
  The \emph{universal abelian covering quiver} $\hat Q$ of $Q$ has vertices $\hat Q_0=Q_0\times A_Q$ and arrows $\hat Q_1=Q_1\times A_Q$, where $(\alpha,\chi):\big(s(\alpha),\chi\big)\to\big(t(\alpha),\chi+e_\alpha\big)$ for $\alpha\in Q_1$ and $\chi\in A_Q$.
  Write $F_Q:\rep \hat Q\to\rep Q$ for the natural functor.

@@

We will mainly be interested in particular lifts $\tilde P_m$ of the preprojective representations $P_m$ of $K(n)$ to the universal cover $\widetilde{K(n)}$.
In the notation of Definition~\ref{def:covering quivers}, this means $G(\tilde P_m)=P_m$, where $G$ is the covering functor 
\[G:=G_{K(n)}:\rep\widetilde{K(n)}\to\rep K(n).\]

To construct the lifts, first recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_n}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
The preprojective lifts we use are defined by the following analogue of the recursions of Remark~\ref{rem:reflection recursion}.
\begin{itemize}
  \item For $m=1$, we consider the lift $\tilde P_1$ satisfying $\dim(\tilde P_1)_{(1,1)}=1$ and $\dim (\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,1)$.
  \item For $m=2$, we consider the lift $\tilde P_2$ satisfying $\dim (\tilde P_2)_{(2,1)}=\dim (\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\dim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,1),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
  \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
    More precisely, we set
    \begin{align}
      \label{eq:recursive covers}
      \tilde P_m:=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1},
    \end{align}
    where $(-)^\sigma:\rep\widetilde{K(n)}^{op}\to\rep\widetilde{K(n)}$ is the lift of the corresponding functor for $K(n)$.
\end{itemize}

It will be rather important that our chosen lifts of $\tilde P_{2l}$ and $\tilde P_{2l-1}$, $l\ge1$, live on two different components of the universal covering quiver.
Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation~$\tilde P_m$ by the action of $w\in W_n$.
To simplify the notation, we abbreviate $\tilde P_{2l-1,i}:=\tilde P_{2l-1,\alpha_i}$ and $\tilde P_{2l,i}:=\tilde P_{2l,\alpha_i^{-1}}$.
\begin{lemma}
  For each $m\ge1$, the representation $\tilde P_{m+1}$ has precisely $n$ subrepresentations covering $P_m$.
  These are the representations $\tilde P_{m,i}$ corresponding to the $n$ different arrows of $K(n)$. 
\end{lemma}
\begin{proof}
  This is clear for $m=1$ and follows in general by applying the identities \eqref{eq:recursive covers}.
\end{proof}
\begin{remark}
  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric under permutations of the arrows of $K(n)$ (or rather the corresponding operation on $\widetilde{K(n)}$).
  In particular, they all have the same middle vertex $(1,1)$ if $m$ is odd and middle vertex $(2,1)$ if $m$ is even.
\end{remark}

The next result establishes some basic homological properties of these translated preprojective representations.
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For $j\in\{1,\ldots,n\}$, we have
      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \ses{\bigoplus_{i\in I} \tilde P_{m,i}}{\tilde P_{m+1}}{\tilde P_{m+1}^I}.
      \end{equation}
      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  Part (1) is immediate from Theorem~\ref{covering}.
  Part (2) is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC=\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

  Part (3) is clear for $m=1$ and follows for $m\ge2$ by applying the reflection recursion \eqref{eq:recursive covers}.

  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset H_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$ and the preceding discussion shows that $G(\tilde P_{m+1}^I)\cong P_{m+1}^V$ is truncated preprojective as well.
\end{proof}
In the following, we make use of this lemma and fix a basis of $\Hom(P_m,P_{m+1})$ which is compatible with the direct sum decomposition from part (1).
\begin{lemma}
  \label{le:properties}
  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
  \begin{enumerate}
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\notin I$, in which case 
      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})=\CC.\] 
    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)=\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
      Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\tilde P_{m,j},\tilde P_{m,j})=\CC.\] 
    \item We have $\Hom(P_{m+1}^I,P_{m+1}^I)=\CC$ and $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
      In particular, $P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
    %\item We have $\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=0$ and $\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\CC$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
  where the final zero follows from Lemma~\ref{le:homdecomposition}.(2).
  Now the middle space is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).

  Part (2) is an immediate consequence of Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering} or can be obtained directly by applying $\Hom(\tilde P_{m+1},-)$ to the sequence \eqref{ses1}.
  The first part of (3) follows from Theorem~\ref{covering} together with Lemma~\ref{le:basic homological properties}.
  For the second part of (3), we apply $\Hom(-,\tilde P_{m,j})$ to the sequence \eqref{ses1}.
  Then taking into account Lemma~\ref{le:homdecomposition} part (3), we get the isomorphism
  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\textstyle{\bigoplus_{i\in I}}\tilde P_{m,i},\tilde P_{m,j}).\] 
  Then Lemma~\ref{le:homdecomposition}.(2) gives the final claim of part (3).
  %The Auslender-Reiten formulas \cite[Theorem IV.2.13]{ass} then give part (4).

  Part (4) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} and then using parts (1) and (2).
  %Then the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} imply 
  %\[\dim\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0\]
  %and
  %\[\dim\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=1\]
  %which proves part (6).
\end{proof}

Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
For $l\ge1$, set
\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\}, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
More precisely, we obtain a sequence of preprojective representations which uniquely determines the desired inclusion:
\[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]

Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
For $m\ge3$, define the representation 
\begin{lemma}
  Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
  For $m\ge2$, we have $\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\CC$.
  Moreover, the kernel of the unique morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is the following representation 
  \[\tilde P_m(I,j):=
    \begin{cases}
      \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{m-1,(j,i)}\oplus \bigoplus_{i\in I, i\ne j}\tilde P_{m-2,i} & \text{ if $m\geq 3$;}\\
      \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{1,(j,i)} & \text{ if $m=2$.}
    \end{cases}\]
\end{lemma}
\begin{proof}
  The first claim follows from Lemma~\ref{le:properties}.(3) by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass}.
  Indeed, this gives the isomorphism
  \[\dim\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})=\CC.\]

  We establish the final claim directly for $m=2,3$ and then deduce the general case by applying the reflection recursions \eqref{eq:recursive covers}.
\end{proof}
%Note that by Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
%\[\ses{\bigoplus_{i\in J\setminus I}\tilde P_{m,i}}{\tilde P_m^I}{\tilde P_{m+1}^J}.\]

%In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
%That is, taking $\varepsilon=(-1)^{m+1}$ we quotient out the translations $\tilde P_{m,w\alpha_i^\varepsilon}$ for $i\in I$.
%These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
